A Monte Carlo Synthetic-Acceleration Method for Solving the Thermal Radiation Diffusion Equation\tnoteref{ornl-cr}

### 2013-05-16 doc/jcomp2012/response.txt

Dear Editor,

     Thank you for the thorough reviews to our paper.  We hope that we have
     successfully responded to each reviewer.  Our responses follow below:

     Response to reviewer 2.

     We have added an acknowledgement indicating that the early part of the
     work was performed at LANL.  We have added Section 2.4 that does detailed
     comparisons between sequential Monte Carlo and MCSA.  Furthermore, we
     have added text in the discussion that highlights the differences between
     the methods.

     This reviewer made a number of key editorial observations.  We have
     adapted the text for each of them.  Some key points:

     - we added a reference to synthetic acceleration
     - we defined the terms in Eq. 6 and added some text for clarity
     - we didn't add "adjoint" to the abstract because we feel it would be
       confusing to the traditional Monte Carlo transport community.  We feel
       the discussion in the text clarifies the differences sufficiently. We
       also clarified the discussion involving the Kronecker delta in Eq. 13.
     - we chose Np and Wc for the multimaterial problem using numerical
       experiments; we added text indicating this.

     Response to reviewer 3.

     This reviewer correctly observed that the solvers that we compared MCSA
     to in our original manuscript and the way the information was presented
     was deficient.  We have expanded the results section to include GMRES and
     CG results with a family of state-of-the-art preconditioners.  We also
     updated the tables to include average and total iterations along with
     other useful quantities that makes the comparisons more meaningful.
     Additional text has been added to the results section to clarify the
     comparisons.

     We added a sentence clarifying the use of +|- in Eq 51.

     We added a paragraph providing more motivation to the introduction.

     We presented Figure 11 showing the spectral radius as a function of
     problem time in order to address the issue of variable time-step size
     versus solver performance.  Because all solvers use the same time-steps,
     no additional parameterization studies should be required.  We do
     appreciate that different solvers can behave differently based on
     time-step size, we feel that for this model equation, we are capturing
     the comparison between each method fairly.

### 2013-05-16 doc/jcomp2012/jcomp2012.tex
Final edits.

    We present a novel synthetic-acceleration-based Monte Carlo method for
    solving the equilibrium thermal radiation diffusion equation in three
    spatial dimensions. The algorithm performance is compared against
    traditional solution techniques using a Marshak benchmark problem and a
    more complex multiple material problem. Our results show that our Monte
    Carlo method is an effective solver for sparse matrix systems. For
    solutions converged to the same tolerance, it performs competitively with
    deterministic methods including preconditioned conjugate gradient. We also
    discuss various aspects of preconditioning the method and its general
    applicability to broader classes of problems.

@@

\subsection{Comparison to Sequential Monte Carlo}
\label{subsec:sequential_comparison}
To further motivate using Monte Carlo Synthetic Acceleration, we compare its
performance to Halton's sequential Monte Carlo method on which our previous
work in this area was based. For this comparison, we use the same transient
Poisson problem as described in the previous section and choose only the
5-point stencil to discretize the Laplacian operator as the previous results
yielded little qualitative difference between the discretizations. Both MCSA
and Halton's method are used with the adjoint Monte Carlo solver. In order to
complete the same study as in the previous section, the number of histories
computed by the Monte Carlo solver at each iteration had to be doubled to $2
\times N \times N$ in order to ensure convergence in sequential Monte Carlo
Method. Figure~\ref{fig:seq_cpu_time} gives the CPU time results for this
comparison as a function of problem size while Figure~\ref{fig:seq_iterations}
gives the number of iterations to converge as a function of problem size. In
both cases, using the Monte Carlo solver as a synthetic acceleration rather
than in a sequential Monte Carlo scheme resulted in a reduction in both CPU
time and iterations required to converge. The additional Richardson iteration
between each Monte Carlo solve in the MCSA method gives a better converged
residual source to use with the Monte Carlo calculation while the sequential
method requires more iterations to achieve the same level of convergence in
the residual.

@@

The benefits of using a synthetic acceleration scheme are also noted when the
infinity norm of the residual computed at each iteration for both methods was
collected at each iteration for a fixed problem sizes of $N=100$ and $N=500$
as shown in figures Figure~\ref{fig:seq_100} and \ref{fig:seq_500}
respectively. In both cases, the sequential method is characterized by a slow
approach to the asymptotic rate of convergence.  Conversely, the MCSA method
reaches its asymptotic convergence rate more quickly and is faster than
Halton's method. Even with the doubling of the number of stochastic histories
computed per time step in order to ensure convergence for the sequential
method, we still see robustness issues with a non-monotonically decreasing
residual observed for the $N=100$ case. In both cases the MCSA solver is
observed to be robust with a monotonically decreasing residual.

@@

Using Fick's Law, Eq.~(\ref{eq:fick}), we can write $O(\Delta^2)$ expressions
for the face-centered fluxes.  Defining $l\in\{i,j,k\}$, the face-centered
fluxes are
\begin{align}
  F_{l+1/2} &= -D_{l+1/2}\frac{\phi_{l+1} -
    \phi_{l}}{\Delta_{l+1/2}}\:, \label{eq:F_l+1/2}\\ F_{l-1/2} &=
  -D_{l-1/2}\frac{\phi_{l} -
    \phi_{l-1}}{\Delta_{l-1/2}}\:, \label{eq:F_l-1/2}
\end{align}
where
\begin{align}
  \Delta_{l+1/2} &= \frac{\Delta_{l+1} +
    \Delta_{l}}{2}\:,\\ \Delta_{l-1/2} &= \frac{\Delta_{l} +
    \Delta_{l-1}}{2}\:.
\end{align}
In order to be conservative, the flux must be continuous across a face.  Thus,
the face-centered flux evaluated from either side of the face must be
equivalent:
\begin{equation}
  \begin{aligned}
    F_{l+1/2}^{+} &= F_{l+1/2}^{-}\:,\\ 2D_{l+1}\frac{\phi_{l+1} -
      \phi_{l+1/2}}{\Delta_{l+1}} &= 2D_{l}\frac{\phi_{l+1/2} -
      \phi_{l}}{\Delta_l}\:,\\ \frac{1}{3\sigma_{l+1}}\frac{\phi_{l+1}
      - \phi_{l+1/2}}{\Delta_{l+1}} &=
    \frac{1}{3\sigma_{l}}\frac{\phi_{l+1/2} - \phi_{l}}{\Delta_l}\:,
  \end{aligned}
\end{equation}
where we have dropped the subscript $\mathrm{R}$ from $\sigma$ for clarity.
Solving this system for $\phi_{l+1/2}$ and applying to either $F_{l+1/2}^{+}$
or $F_{l+1/2}^{-}$ and setting the resulting expression equal to
Eq.~(\ref{eq:F_l+1/2}), one finds the face-centered diffusion coefficient,
\begin{equation}
  D_{l+1/2} = \frac{2\Delta_{l+1/2}}{3\sigma_l\Delta_l +
    3\sigma_{l+1}\Delta_{l+1}}\:.
  \label{eq:D_l+1/2}
\end{equation}
Following the same procedure at the $l-1/2$ face gives the diffusion
coefficient on the low-side face:
\begin{equation}
  D_{l-1/2} = \frac{2\Delta_{l-1/2}}{3\sigma_l\Delta_l +
    3\sigma_{l-1}\Delta_{l-1}}\:.
  \label{eq:D_l-1/2}
\end{equation}

@@

First, we use Eq.~(\ref{eq:preconditioned-discrete-diffusion}) to evaluate
$\bphi^{l+1/2}$ via a single fixed-point iteration as follows:
\begin{equation}
  \begin{aligned}
    \phi_{ijk}^{l+1/2} =
    \frac{\sigm_{i+1}}{\sigT}\frac{\Delta_{i+1}}{\Di}&\phi_{i+1\,jk}^l
    +
    \frac{\sigp_{i-1}}{\sigT}\frac{\Delta_{i-1}}{\Di}\phi_{i-1\,jk}^l
    \\ &+
    \frac{\sigm_{j+1}}{\sigT}\frac{\Delta_{j+1}}{\Dj}\phi_{i\,j+1\,k}^l
    +
    \frac{\sigp_{j-1}}{\sigT}\frac{\Delta_{j-1}}{\Dj}\phi_{i\,j-1\,k}^l
    \\ &+
    \frac{\sigm_{k+1}}{\sigT}\frac{\Delta_{k+1}}{\Dk}\phi_{ij\,k+1}^l
    +
    \frac{\sigp_{k-1}}{\sigT}\frac{\Delta_{k-1}}{\Dk}\phi_{ij\,k-1}^l
    + \frac{\qn_{ijk}}{\sigT}\:.
  \end{aligned}
\end{equation}
This result is used to compute the residual of the system.  The residual then
becomes the source for the Monte Carlo simulation.

The adjoint Monte Carlo method described in \S~\ref{sec:adjoint-method} is
used to estimate
\begin{equation}
  \ve{M}^{-1}\hat{\ve{D}}\delta\bphi^{l+1/2} = \vr^{l+1/2}\:.
\end{equation}
As noted above, the residual acts as the source for this simulation, and the
operator $\ve{T}$ is implicitly defined in
Eq.~(\ref{eq:preconditioned-discrete-diffusion}).  There are two Monte Carlo
interpretations that can be applied to this system.  The first follows the
mathematical presentation given in \S~\ref{sec:monte-carlo-matrix}.  Namely,
we form probabilities from the iteration matrix and perform random walks to
generate unbiased estimates of the solution vector, $\delta\bphi^{l+1/2}$,
using the estimator in Eq.~(\ref{eq:adjoint-tally}).

@@

Here we examine the effectiveness of the MCSA method and compare it to
traditional deterministic solution methods.  We implemented Krylov subspace
methods to solve the radiation diffusion equation using the Trilinos solver
library \cite{1089021}.  Conjugate Gradient (CG) is that standard method for
symmetric positive-definite (SPD) systems like that defined in
Eq.~(\ref{eq:discrete-diffusion}).  However, for completeness we include some
comparisons using restarted GMRES($m$) so that asymmetric preconditioners can
be tested. The stopping criterion in Eq.~(\ref{eq:stopping-criteria}) is used
for all calculations. All methods are tested on two 3D problems: a
uniform-medium Marshak wave problem and a multi-material duct problem.

@@

Having analyzed the variation of the MCSA algorithm efficiency with number of
particles and weight cutoff, we now compare to traditional deterministic
algorithms.  Table~\ref{tab:marshak_comparison} shows timing results for the
Marshak problem using CG with Jacobi and algebraic multigrid preconditioning
and GMRES with incomplete LU (ILU) and ILU with threshold cutoff (ILUT).  The
multigrid preconditioner is the smoothed aggregation algebraic multigrid
method implemented in the Trilinos ML package \cite{Gee:2007uj}.  In all the
problems that follow we use a $4/3$ damping factor in the aggregation and a
symmetric Gauss-Seidel smoother with 2 sweeps per level.

Analyzing Table~\ref{tab:marshak_comparison}, we see that the overall
iterations are more than a factor of 2 less for the Krylov solvers compared to
MCSA; however, the cost per iteration is signicantly more expensive.  For any
given problem, the cost per iteration is roughly linear with particle count as
illustrated in Fig.~\ref{fig:CPU_Np}.  Because this problem converges running
only a maximum of 10 particles per iteration, 156,464 total particles over
10,157 cycles resulting in an average of $\sim 1.6$ particles per iteration,
the cost per iteration is exceptionally small.  Running more particles per
iteration would reduce the number of iterations, but a greater cost per
iteration.
\begin{table}[ht!]
  \caption{Comparison of solution methods for the Marshak problem. All
    methods were run with a stopping criterion of $\sn{1}{-8}$.  The
    MCSA method used $N_p=10$ and $W_c = \sn{1}{-4}$.   Runtimes are relative
    to the MCSA performance that required 57.72 seconds on
    an 2.2 MHz AMD Opteron.}
  \label{tab:marshak_comparison}
  \begin{center}
    \small
    \begin{tabular}{llrrrr}\hline\hline
      \multicolumn{1}{c}{Method} &
      \multicolumn{1}{c}{Preconditioner} &
      \multicolumn{1}{c}{Total} &
      \multicolumn{1}{c}{Average} &
      \multicolumn{1}{c}{Relative Time} &
      \multicolumn{1}{c}{Relative}\\
      & & \multicolumn{1}{c}{Iterations} &
      \multicolumn{1}{c}{Iterations} &
      \multicolumn{1}{c}{per Iteration} &
      \multicolumn{1}{c}{Runtime} \\\hline\hline
      %%
      CG & Jacobi & 46,746 & 4.60 & 25.91 & 3.29 \\
      CG & ML & 12,150 & 1.20 & 74.72 & 2.69 \\
      GMRES & ILU & 40,294 & 3.97 & 103.02 & 9.19 \\
      GMRES & ILUT$^{\dagger}$ & 40,447 & 3.98 & 101.31 & 9.09 \\
      MCSA & Jacobi & 98,863 & 9.73 & 1.0 & 1.0
      %%
      \\ \hline\hline
      \multicolumn{6}{l}{
        $^{\dagger}$ The threshold cutoff was set to 0.01, and the fill was 1.}
    \end{tabular}
  \end{center}
\end{table}

@@

We have presented a new Monte Carlo solution method for solving the discrete,
time-dependent radiation diffusion equation in three dimensions.  The MCSA
method has been shown to match results using standard solution techniques to
arbitrary precision. Also, the new method has been to shown to be faster than
preconditioned CG and Richardson iteration for the model problems presented
here.

@@

@@

Work for this paper was supported by Oak Ridge National Laboratory, which is
managed and operated by UT-Batelle, LLC, for the U.S. Department of Energy under
Contract No. DEAC05-00OR22725.

>>>>

    We present a novel synthetic-acceleration-based Monte Carlo method for
    solving the equilibrium thermal radiation diffusion equation in three
    spatial dimensions. The algorithm performance is compared against
    traditional solution techniques using a Marshak benchmark problem and a
    more complex multiple material problem. Our results show that our Monte
    Carlo method is an effective solver for sparse matrix systems. For
    solutions converged to the same tolerance, it performs competitively with
    deterministic methods including preconditioned conjugate gradient and
    GMRES. We also discuss various aspects of preconditioning the method and
    its general applicability to broader classes of problems.

@@

\subsection{Comparison to Sequential Monte Carlo}
\label{subsec:sequential_comparison}
To further motivate using Monte Carlo Synthetic Acceleration, we compare its
performance to Halton's sequential Monte Carlo method on which our previous
work in this area was based. For this comparison, we use the same transient
Poisson problem as described in the previous section and choose only the
5-point stencil to discretize the Laplacian operator as the previous results
yielded little qualitative difference between the discretizations. Both MCSA
and Halton's method are used with the adjoint Monte Carlo solver. In order to
complete the same study as in the previous section, the number of histories
computed by the Monte Carlo solver at each iteration had to be doubled to $2
\times N \times N$ in order to ensure convergence when using the sequential
Monte Carlo Method. Figure~\ref{fig:seq_cpu_time} gives the CPU time results
for this comparison as a function of problem size while
Figure~\ref{fig:seq_iterations} gives the number of iterations to converge as
a function of problem size. In both cases, using the Monte Carlo solver as a
synthetic acceleration rather than in a sequential Monte Carlo scheme resulted
in a reduction in both CPU time and iterations required to converge. The
additional Richardson iteration between each Monte Carlo solve in the MCSA
method gives a better converged residual source to use with the Monte Carlo
calculation while the sequential method requires more iterations to achieve
the same level of convergence in the residual.

@@

The benefits of using a synthetic acceleration scheme are also noted when the
infinity norm of the residual computed at each iteration for both methods was
collected at each iteration for a fixed problem sizes of $N=100$ and $N=500$
as shown in figures Figure~\ref{fig:seq_100} and \ref{fig:seq_500}
respectively. In both cases, the sequential method is characterized by a slow
approach to the asymptotic rate of convergence.  Conversely, MCSA reaches its
asymptotic convergence rate more quickly and exhibits a faster final rate of
convergence than Halton's method. Even with the doubling of the number of
stochastic histories computed per time step in order to ensure convergence for
the sequential method, we still see robustness issues with a non-monotonically
decreasing residual observed for the $N=100$ case. In both cases the MCSA
solver is observed to be robust with a monotonically decreasing residual.

@@

Using Fick's Law, Eq.~(\ref{eq:fick}), we can write $O(\Delta^2)$ expressions
for the face-centered fluxes.  Defining $l\in\{i,j,k\}$, the face-centered
fluxes are
\begin{align}
  F_{l+1/2} &= -D_{l+1/2}\frac{\phi_{l+1} -
    \phi_{l}}{\Delta_{l+1/2}}\:, \label{eq:F_l+1/2}\\ F_{l-1/2} &=
  -D_{l-1/2}\frac{\phi_{l} -
    \phi_{l-1}}{\Delta_{l-1/2}}\:, \label{eq:F_l-1/2}
\end{align}
where
\begin{align}
  \Delta_{l+1/2} &= \frac{\Delta_{l+1} +
    \Delta_{l}}{2}\:,\\ \Delta_{l-1/2} &= \frac{\Delta_{l} +
    \Delta_{l-1}}{2}\:.
\end{align}
In order to be conservative, the flux must be continuous across a face.  Thus,
the face-centered flux evaluated from either side of the face must be
equivalent:
\begin{equation}
  \begin{aligned}
    F_{l+1/2}^{+} &= F_{l+1/2}^{-}\:,\\ 2D_{l+1}\frac{\phi_{l+1} -
      \phi_{l+1/2}}{\Delta_{l+1}} &= 2D_{l}\frac{\phi_{l+1/2} -
      \phi_{l}}{\Delta_l}\:,\\ \frac{1}{3\sigma_{l+1}}\frac{\phi_{l+1}
      - \phi_{l+1/2}}{\Delta_{l+1}} &=
    \frac{1}{3\sigma_{l}}\frac{\phi_{l+1/2} - \phi_{l}}{\Delta_l}\:,
  \end{aligned}
\end{equation}
where we have dropped the subscript $\mathrm{R}$ from $\sigma$ for clarity and
the $\pm$ superscripts indicate positive and negative directions across the
face.  Solving this system for $\phi_{l+1/2}$ and applying to either
$F_{l+1/2}^{+}$ or $F_{l+1/2}^{-}$ and setting the resulting expression equal
to Eq.~(\ref{eq:F_l+1/2}), one finds the face-centered diffusion coefficient,
\begin{equation}
  D_{l+1/2} = \frac{2\Delta_{l+1/2}}{3\sigma_l\Delta_l +
    3\sigma_{l+1}\Delta_{l+1}}\:.
  \label{eq:D_l+1/2}
\end{equation}
Following the same procedure at the $l-1/2$ face gives the diffusion
coefficient on the low-side face:
\begin{equation}
  D_{l-1/2} = \frac{2\Delta_{l-1/2}}{3\sigma_l\Delta_l +
    3\sigma_{l-1}\Delta_{l-1}}\:.
  \label{eq:D_l-1/2}
\end{equation}

@@

First, we use Eq.~(\ref{eq:preconditioned-discrete-diffusion}) to evaluate
$\bphi^{l+1/2}$ via a single fixed-point iteration as follows:
\begin{equation}
  \begin{aligned}
    \phi_{ijk}^{l+1/2} =
    \frac{\sigm_{i+1}}{\sigT}\frac{\Delta_{i+1}}{\Di}&\phi_{i+1\,jk}^l
    +
    \frac{\sigp_{i-1}}{\sigT}\frac{\Delta_{i-1}}{\Di}\phi_{i-1\,jk}^l
    \\ &+
    \frac{\sigm_{j+1}}{\sigT}\frac{\Delta_{j+1}}{\Dj}\phi_{i\,j+1\,k}^l
    +
    \frac{\sigp_{j-1}}{\sigT}\frac{\Delta_{j-1}}{\Dj}\phi_{i\,j-1\,k}^l
    \\ &+
    \frac{\sigm_{k+1}}{\sigT}\frac{\Delta_{k+1}}{\Dk}\phi_{ij\,k+1}^l
    +
    \frac{\sigp_{k-1}}{\sigT}\frac{\Delta_{k-1}}{\Dk}\phi_{ij\,k-1}^l
    + \frac{\qn_{ijk}}{\sigT}\:.
  \end{aligned}
\end{equation}
This result is used to compute the residual of the system that, in turn,
becomes the source for the Monte Carlo simulation.

The adjoint Monte Carlo method described in \S~\ref{sec:adjoint-method} is
used to estimate
\begin{equation}
  \hat{\ve{T}}\delta\bphi^{l+1/2} = \vr^{l+1/2}\:.
\end{equation}
As noted above, the residual acts as the source for this simulation, and the
operator $\ve{T}$ is implicitly defined in
Eq.~(\ref{eq:preconditioned-discrete-diffusion}).  There are two Monte Carlo
interpretations that can be applied to this system.  The first follows the
mathematical presentation given in \S~\ref{sec:monte-carlo-matrix}.  Namely,
we form probabilities from the iteration matrix and perform random walks to
generate unbiased estimates of the solution vector, $\delta\bphi^{l+1/2}$,
using the estimator in Eq.~(\ref{eq:adjoint-tally}).

@@

Here we examine the effectiveness of the MCSA method and compare it to
traditional deterministic solution methods.  We implemented Krylov subspace
methods to solve the radiation diffusion equation using the Trilinos solver
library \cite{1089021}.  Conjugate Gradient (CG) is the standard method for
symmetric positive-definite (SPD) systems like that defined in
Eq.~(\ref{eq:discrete-diffusion}).  However, for completeness we include some
comparisons using restarted GMRES($m$) so that asymmetric preconditioners can
be tested. The stopping criterion in Eq.~(\ref{eq:stopping-criteria}) is used
for all calculations. All methods are tested on two 3D problems: a
uniform-medium Marshak wave problem and a multi-material duct problem.

@@

Having analyzed the variation of the MCSA algorithm efficiency with number of
particles and weight cutoff, we now compare to traditional deterministic
algorithms.  Table~\ref{tab:marshak_comparison} shows timing results for the
Marshak problem using CG with Jacobi and algebraic multigrid preconditioning
and GMRES with incomplete LU (ILU) and ILU with threshold cutoff (ILUT). The
Krylov methods and preconditioners are implemented throught the Trilinos
AztecOO package.  The multigrid preconditioner is the smoothed aggregation
algebraic multigrid method implemented in the Trilinos ML package
\cite{Gee:2007uj}.  In all the problems that follow we use a $4/3$ damping
factor in the aggregation and a symmetric Gauss-Seidel smoother with 2 sweeps
per level, which are the defaults for the ML smoothed aggregation option.

Analyzing Table~\ref{tab:marshak_comparison}, we see that the overall
iterations are more than a factor of 2 less for the Krylov solvers compared to
MCSA; however, the cost per iteration is signicantly more expensive.  For any
given problem, the cost per iteration is roughly linear with particle count as
illustrated in Fig.~\ref{fig:CPU_Np}.  Because this problem converges running
only a maximum of 10 particles per iteration, 156,464 total particles over
10,157 cycles resulting in an average of $\sim 1.6$ particles per iteration,
the cost per iteration is exceptionally small.  Running more particles per
iteration would reduce the number of iterations, but at a greater cost per
iteration.
\begin{table}[ht!]
  \caption{Comparison of solution methods for the Marshak problem. All
    methods were run with a stopping criterion of $\sn{1}{-8}$.  The
    MCSA method used $N_p=10$ and $W_c = \sn{1}{-4}$.   Runtimes are relative
    to the MCSA performance that required 57.72 seconds on
    an 2.2 MHz AMD Opteron.}
  \label{tab:marshak_comparison}
  \begin{center}
    \small
    \begin{tabular}{llrrrr}\hline\hline
      \multicolumn{1}{c}{Method} &
      \multicolumn{1}{c}{Preconditioner} &
      \multicolumn{1}{c}{Total} &
      \multicolumn{1}{c}{Average} &
      \multicolumn{1}{c}{Relative Time} &
      \multicolumn{1}{c}{Relative}\\
      & & \multicolumn{1}{c}{Iterations} &
      \multicolumn{1}{c}{Iterations} &
      \multicolumn{1}{c}{per Iteration} &
      \multicolumn{1}{c}{Runtime} \\\hline\hline
      %%
      CG & Jacobi & 46,746 & 4.60 & 25.91 & 3.29 \\
      CG & ML & 12,150 & 1.20 & 74.72 & 2.69 \\
      GMRES & ILU & 40,294 & 3.97 & 103.02 & 9.19 \\
      GMRES & ILUT$^{\dagger}$ & 40,447 & 3.98 & 101.31 & 9.09 \\
      MCSA & Jacobi & 98,863 & 9.73 & 1.0 & 1.0
      %%
      \\ \hline\hline
      \multicolumn{6}{l}{
        $^{\dagger}$ The threshold cutoff was set to 0.01, and the fill was 1.}
    \end{tabular}
  \end{center}
\end{table}

@@

We have presented a new Monte Carlo solution method for solving the discrete,
time-dependent radiation diffusion equation in three dimensions.  The MCSA
method has been shown to match results using standard solution techniques to
arbitrary precision. Also, the new method has been to shown to be faster than
preconditioned CG and GMRES for the model problems presented here.

@@

Finally, exascale hardware will require resiliency to both hard and soft
errors.  Stochastic solver approaches present a natural framework for both
soft and hard errors.  In the former case, soft errors can be presented as
high variance events.  For hard errors, histories from failed nodes can be
safely discarded in the final calculation. The MCSA method provides a starting
framework towards analyzing both of these failure conditions.

@@

Work for this paper was supported by Oak Ridge National Laboratory, which is
managed and operated by UT-Batelle, LLC, for the U.S. Department of Energy
under Contract No. DEAC05-00OR22725.  The early part of this work was
performed at Los Alamos National Laboratory under U.S. Government contract
W-7405-ENG-36.
